Effects of Reynolds Number on the Performance and Near-Wake of a Vertical-Axis Cross-Flow Turbine

### 2015-04-17 paper.tex
Add to wake results section

\subsubsection{Dominant Timescales}

@@

\subsubsection{Mean Momentum and Kinetic Energy Transport}

@@

The relative importance of various physical processes on mean kinetic energy
transport/recovery in the streamwise direction $\p K / \p x$ are plotted in...

@@

>>>>

\subsubsection{Dominant Timescales and Turbulence Spectra}

@@

\subsubsection{Transport of Mean Momentum and Kinetic Energy}

The relative importance of various physical processes on mean streamwise
momentum and kinetic energy transport/recovery in the streamwise direction are
plotted in Figures~\ref{fig:mom-bar-graph} and \ref{fig:K-bar-graph},
respectively. We note that similar to \cite{Bachant2015-JoT}, the vertical
advection at this point in the wake is the dominant contributor to positive wake
recovery, caused by the unique vortex pattern created by the blade tips and
wakes.

We see that in general, levels of turbulent transport are slightly lower at
lower Reynolds numbers. The viscous diffusion and dissipation, though still
three orders of magnitude smaller than the other terms, do increase at low
Reynolds numbers, which is consistent with the definition of the Reynolds number
in general.

\todo[inline]{At what $Re$ will the viscous terms get large enough to start
messing with the balance of the equation?}

@@

@@

Totals for all the wake transport terms calculated are plotted in
Figure~\ref{fig:wake-trans-totals}. We see that in general wake transport is
enhanced at lower Reynolds numbers and levels off consistent with the power
coefficient data. This is an important consideration if studying sub-scale
models of turbine arrays, where increased levels of wake recovery will motivate
different ideal array configurations when compared with full-scale turbines.
